Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-12-05 grove-paper.tex
add implementation notes on tree decomp

>>>>

Related: hypertree decomposition is an established topic in AI/DB. Apparently,
it's NP-complete in general, so people look for tractable subproblems. Recent
work focuses on reduction to SMT and parallelizability for large db-like
querying of large graphs, but some papers also focus on efficient decompopsition
for "nearly acyclic" graphs. The closest I could find to what we're already
doing are the k-decomp / opt-k-decomp / det-k-decomp algoriths in this paper:
https://dl.acm.org/doi/10.1145/1412228.1412229, except we're getting determinism
for free (i.e., not having to guess-and-check pivot points) by virtue of our
global root and uuid-based total ordering on basically everything.
